Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-10-29 paper/1_Initial/manuscript.qmd
Summarised measures
@DominiqueMakowski

<!-- Mood and Anxiety -->
#### Mood and Anxiety Related
The Beck Depression Inventory-II [BDI-II, @beck1996beck] is a 21-item measure of depressive symptom severity, including psychological (e.g., guilt) and physiological (e.g., loss of energy) components. Items are rated on a 4-point scale (e.g., “I feel sad much of the time”).

@@

The Generalized Anxiety Disorder Scale [GAD-7, @spitzer2006brief] is a 7-item measure of generalized anxiety symptoms rated on a 4-point Likert scale (e.g., “Not being able to stop or control worrying”).

<!-- Personality -->
#### Personality
The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992personality] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust. Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).

The Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring] is a 10-item measure of the Big Five traits, rated on a 7-point Likert scale (e.g., “I see myself as someone who … is considerate and kind to almost everyone”).

@@

#### Psychopathology
The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).

@@

The Autism Spectrum Quotient Short Form [ASQ-S, @hoekstra2011construction] is a 28-item measure of five autistic traits: social skills, adherence to routines, cognitive flexibility, imagination, and patterns/numbers. Items are rated on a 4-point Likert scale (e.g., “I find it difficult to work out people’s intentions”).

<!-- Beliefs and Misbeliefs -->
#### Beliefs and Misbeliefs
The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information. Items are scored on a 5-point Likert scale (e.g., “Secret organizations communicate with extraterrestrials, but keep this fact from the public”).

@@

The Lie Scale [LIE, @makowski2023structure] is a 16-item measure of lying tendencies across four components: Ability, Frequency, Negativity, and Contextuality. Items are scored on visual analogue scales (e.g., “I am a good liar”).

>>>>

<!-- Mood and Anxiety -->
#### Mood and Anxiety Related
Mood-related measures included the Beck Depression Inventory-II [BDI-II, @beck1996beck], the Patient Health Questionnaire-4 [PHQ-4, @kroenke2009ultra], the Patient Health Questionnaire-9 [PHQ-9, @kroenke2001phq], the Patient Health Questionnaire-15 [PHQ-15, @kroenke2002phq], the Short Mood and Feelings Questionnaire [SMFQ, @angold1995development], the State–Trait Anxiety Inventory Trait Version [STAI-T, @spielberger1970manual], and the Generalized Anxiety Disorder Scale [GAD-7, @spitzer2006brief]. We also included the PHQ-2 [@kroenke2003patient] and General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety], which were combined with the PHQ-4 scores, and scores from the shorter version of the STAIT-5 [@zsido2020development], which were combined with the STAI-T. Mood measures were included given the well-established association between interoceptive deficits and mental health conditions [@khalsa2018].

<!-- 
The Beck Depression Inventory-II [BDI-II, @beck1996beck] is a 21-item measure of depressive symptom severity, including psychological (e.g., guilt) and physiological (e.g., loss of energy) components. Items are rated on a 4-point scale (e.g., “I feel sad much of the time”).

@@

The Generalized Anxiety Disorder Scale [GAD-7, @spitzer2006brief] is a 7-item measure of generalized anxiety symptoms rated on a 4-point Likert scale (e.g., “Not being able to stop or control worrying”). -->

@@

#### Psychopathology
Personality pathology-related measures included the Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality], the Schizotypal Personality Questionnaire – Brief Revised [SPQ-BR, @davidson2016schizotypal], the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD, @zanarini2003zanarini], and the Autism Spectrum Quotient Short Form [ASQ-S, @hoekstra2011construction]. Similarily, these measures were included due to established associations between various psychopathologies and interoceptive disruptions [@leao2025interoception].

<!-- The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).

@@

The Autism Spectrum Quotient Short Form [ASQ-S, @hoekstra2011construction] is a 28-item measure of five autistic traits: social skills, adherence to routines, cognitive flexibility, imagination, and patterns/numbers. Items are rated on a 4-point Likert scale (e.g., “I find it difficult to work out people’s intentions”). -->

<!-- Personality -->
#### Personality
Personality-related measures included the NEO Five-Factor Inventory, Neuroticism subscale [NEO-FFI, @costa1992personality], the Mini International Personality Item Pool [MINI-IPIP6, @sibley2011mini], and the Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring]. Although associations between personality and interoception have been less frequently explored than those involving mood or psychopathology, previous research has identified links between neuroticism and extroversion and interoceptive sensibility using the MAIA and BPQ measures. This study therefore included extended personality measures to clarify the broader relationships between interoception and personality traits beyond neuroticism and extraversion [@pearson2022two].

<!-- The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992personality] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust. Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).

The Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring] is a 10-item measure of the Big Five traits, rated on a 7-point Likert scale (e.g., “I see myself as someone who … is considerate and kind to almost everyone”). -->

<!-- Beliefs and Misbeliefs -->
#### Beliefs and Misbeliefs
Beliefs- and misbeliefs-related measures included the Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring], the Primal World Beliefs Inventory [PI-99, @clifton2019primal] and its short form [PI-18, @clifton2021brief], and the Lie Scale [LIE, @makowski2023structure]. These instruments assess individual differences in conspiracist, world, and lying beliefs. This domain represents a novel avenue of research in the context of interoception, as such beliefs have not been previously assessed in relation to interoceptive processes.

<!-- The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information. Items are scored on a 5-point Likert scale (e.g., “Secret organizations communicate with extraterrestrials, but keep this fact from the public”).

@@

The Lie Scale [LIE, @makowski2023structure] is a 16-item measure of lying tendencies across four components: Ability, Frequency, Negativity, and Contextuality. Items are scored on visual analogue scales (e.g., “I am a good liar”). -->
